Large Linear Multi-output Gaussian Process Learning for Time Series

### 2017-10-13 paper/paper.tex
a minor paper bug

\begin{figure}[!ht]
\begin{center}
$$
\begin{array}{c}
K_{i\Delta_x\times Y,j\Delta_x\times Y}=\mat{{\color{red} k\pa{\abs{i-j}\Delta_x} }&{\color{blue}\ddots} \\
{\color{blue}\ddots} &{ \color{red} k\pa{\abs{i-j}\Delta_x}} } \\
K_U=\mat{
 {\color{red} K_{0\times Y} } & {\color{blue} K_{0\times Y,\Delta_x\times Y}}& {\color{green}\ddots }\\
{\color{blue} K_{\Delta_x\times Y, 0\times Y}} & {\color{red} K_{\Delta_x\times Y}} & {\color{blue} K_{0\times Y, \Delta_x\times Y}} \\
{\color{green} \ddots } & {\color{blue}  K_{2\Delta_x\times Y, \Delta_x\times Y}} & {\color{red} K_{\Delta_x\times Y}}
}
\end{array}
$$
\end{center}
\caption{An illustration of a stationary kernel $K((a, b), (c, d))=k\pa{\norm{(a-c, b-d)}}$ evaluated on a two-dimensional input grid $U=X\times Y =\{x_i\}\times \{y_j\}$ with separations $\Delta_x,\Delta_y$, resulting in BTTB structure (here, with $\card{X}=3$). Identical matrices are colored the same. We use the shorthand $K_Z=K_{Z,Z}$.}
\label{fig:bttb}
\end{figure}

>>>>

\begin{figure}[!ht]
\begin{center}
$$
\begin{array}{c}
K_{i\Delta_x\times Y,j\Delta_x\times Y}=\mat{{\color{red} k\pa{\abs{i-j}\Delta_x} }&{\color{blue}\ddots} \\
{\color{blue}\ddots} &{ \color{red} k\pa{\abs{i-j}\Delta_x}} } \\
K_U=\mat{
 {\color{red} K_{0\times Y} } & {\color{blue} K_{0\times Y,\Delta_x\times Y}}& {\color{green}\ddots }\\
{\color{blue} K_{\Delta_x\times Y, 0\times Y}} & {\color{red} K_{\Delta_x\times Y}} & {\color{blue} K_{\Delta_x\times Y, 2\Delta_x\times Y}} \\
{\color{green} \ddots } & {\color{blue}  K_{2\Delta_x\times Y, \Delta_x\times Y}} & {\color{red} K_{2\Delta_x\times Y}}
}
\end{array}
$$
\end{center}
\caption{An illustration of a stationary kernel $K((a, b), (c, d))=k\pa{\norm{(a-c, b-d)}}$ evaluated on a two-dimensional input grid $U=X\times Y =\{x_i\}\times \{y_j\}$ with separations $\Delta_x,\Delta_y$, resulting in BTTB structure (here, with $\card{X}=3$). Identical matrices are colored the same. We use the shorthand $K_Z=K_{Z,Z}$.}
\label{fig:bttb}
\end{figure}
